---
output: 
  pdf_document:
    includes: 
      in_header: style.tex
fontsize: 11pt
subparagraph: yes
---

```{r setup, include=FALSE}
source("global.R")
form = "Curriculum Vitae"
```

\lfoot{\textcolor{gray}{J.M. Johnson}}  
\cfoot{\textcolor{gray}{`r form`}}
\rfoot{\textcolor{black}{\thepage}} 
\renewcommand{\footrulewidth}{0.4pt}
\futurelet\TMPfootrule\def\footrule{\color{gray}{\TMPfootrule}}

 \centerline{\LARGE {{\textbf{J. MICHAEL JOHNSON }}}}
 \vspace{3mm}
 \centerline{\textsl{`r form` $\cdot$ `r today`}}
 \vspace{2mm}
 \centerline{\textcolor{gray}{University of California, Santa Barbara, California $\cdot$ Department of Geography}}
 \vspace{2mm}
 

\centerline{\textcolor{header_blue}{\textcolor{gray}{\faGlobe} \hspace{0.2mm} \url{ https://mikejohnson51.github.io}} $\cdot$
             \textcolor{gray}{\faEnvelope} \hspace{0.2mm} jmj00@ucsb.edu $\cdot$
             \textcolor{header_blue}{\textcolor{gray}{\faGithub} \hspace{0.2mm} \url{ https://github.com/mikejohnson51}}
             }

             
\vspace{4mm}
  
\begin{center}  
\begin{mybox}{Keywords:}
\begin{center}
 Geoinformatics (GIS);
 Hydroinformatics;
 Big Data Hydrology;
 Large Scale Modeling
\end{center}
\end{mybox}
\end{center}
\vspace{2mm}

\header{\textbf{EDUCATION}}
\newline
\hspace*{0mm}
\begin{tabular}{p{3cm}P{13.5cm}}
\textbf{March 2021 \newline (Expected)} & \textbf{University of California, Santa Barbara, California (UCSB)} 
\vspace{2mm}
\begin{itemize}
  \item \textbf{Degree:} \hspace{.95cm}PhD Candidate in Geography (ABD)
  \item \textbf{Advisor:} \hspace{.8cm}Dr. Keith C. Clarke
  \item \textbf{Committee:} \hspace{.15cm}Dr. Hugo Loaiciga, Dr. Kelly Caylor, David Blodgett
  \item \textbf{Emphasis:} \hspace{.45cm}Modeling, Measurement, and Computation
  \item \textbf{Title:} \hspace{1.35cm}Spatial Challenges of 21st Century Water Resource Research
\end{itemize}
\vspace{2mm}\\
\textbf{2015} & \textbf{California Polytechnic State University, San Luis Obispo, CA}
\begin{itemize}
  \item \textbf{Degree:} \hspace{.95cm}B.S. Anthropology \& Geography
  \item \textbf{Honors:} \hspace{.95cm}Cum Laude
  \item  \textbf{Minors:} \hspace{.95cm}Geographic Information Systems (GIS) for Agriculture
\newline \tab \tab \hspace{.65cm}Water Science (Watershed Management Emphasis)
\newline \tab \tab \hspace{.65cm}Statistics
\newline \tab \tab \hspace{.65cm}Economics
\newline \tab \tab \hspace{.65cm}Environmental Studies
\end{itemize}
\end{tabular}
\header{{\textbf{RESEARCH EXPERIENCE}}}
\newline
\hspace*{0mm}
\begin{tabular}{p{4cm}P{12cm}}
\textbf{Post-Doctoral Researcher} & \textbf{Center for Spatial Studies, UCSB} 
\begin{itemize}
  \item April 2021 (Offered Start)
\end{itemize}
\vspace{2mm}\\
\textbf{Graduate Student} & \textbf{University of California, Santa Barbara, California (UCSB)} 
\vspace{2mm}

\begin{itemize}
  \item I seek to bridge data-intensive computational geography with water resources research
  \item Work with international and domestic collaborators across academia, the USGS, NCAR, and NOAA 
  \item Develop open source software to ease community access to big data
  \item Served as research coordinator for the NOAA National Water Center Summer Institute
  \item Helped author and am a primary data scientist on a multi-million dollar NSF-funded project
  \item 10 peer-review articles; 2 in revision; 1 in review (8 first author)
  \item 47 citations; h-index 4; i-index 1
\end{itemize}

\end{tabular}

\newpage
\header{PUBLICATIONS}
```{r}
publications = read_excel("mikes-data.xlsx", sheet = "publications") %>% 
  filter(status != "4")

create_subsection <- function(stat) {
  
  cat("\\vspace{-5mm}")
  
  data <- publications %>% 
    filter(status == stat) %>% 
    map_df(rev)
  
  df <- data.frame(citation = paste0(data$authors, '.',
                                   ' (', data$year, '). ',
                                   '{"',  (data$title), '"}', 
                                   ifelse(endsWith(data$title, "?"), ' ', '. '),
                                   ifelse(rep(stat, nrow(data)) == "Working Papers",
                                          paste0(" In preparation", ifelse(!is.na(data$preprint),paste0('\\textsuperscript{1}'),"")),
                                          paste0("\\textit{", data$journal, "}", ifelse(!is.na(data$preprint),paste0('\\textsuperscript{1}'),""))), '. ',
                                   ifelse(is.na(data$link), 
                                          '', 
                                          paste0("\\href{", data$link, "}{Available here.}"))
                                   ))
  
  rownames(df) <- nrow(df):1
  
  print(xtable(df, align = c("r","P{15.5cm}"), caption = paste0("\\hspace{-5mm}", stat)),
      include.rownames = TRUE,
      floating = FALSE)
  
  if(any(!is.na(data$preprint))){
    cat("\\vspace{-4mm}")
    cat('\\tab\\textsuperscript{1}\\textcolor{gray}{Preprint available upon request.}')
    cat("\\vspace{8mm}")
  }
  
}

c("Peer-Reviewed Journal Articles", "In Review Articles", "Technical Reports",  "Cartography") %>% 
  purrr::walk(create_subsection)

cat("\\vspace{-5mm}")

```


\header{RESEARCH GRANTS}
```{r}
grants = read_excel("mikes-data.xlsx", sheet = "funded_research")
grants2 = data.frame(year = grants$date,
                    award = paste0('\\textbf{', grants$name, "} ", "\\newline Role: ",
                                  grants$role, "\\newline ",
                    grants$source, "\\newline ",
                    "\\", scales::dollar(grants$amount)))
   
rownames(grants2) <- nrow(grants2):1     

print(xtable(grants2, align = c("l", "p{4cm}","p{12cm}")),
      tabular.environment = 'longtable',
      floating = FALSE,
      include.rownames = T)

cat("\\vspace{-5mm}")
```

\header{FELLOWSHIPS}

```{r}
fellow = read_excel("mikes-data.xlsx", sheet = "fellowships")
fellow = data.frame(year = fellow$year,
                    award = paste0('\\textbf{', fellow$name, "} ", "\\newline ",
                    fellow$source, "\\newline ",
                    "\\", scales::dollar(fellow$amount)))
                    
rownames(fellow) <- nrow(fellow):1
print(xtable(fellow, align = c("l", "p{2cm}","p{14cm}")),
      tabular.environment = 'longtable',
      floating = FALSE,
      include.rownames = T)


cat("\\vspace{-5mm}")
```

\header{SCIENTIFIC SOFTWARE}

```{r}
cat("\\vspace{2mm}")
software = read_excel("mikes-data.xlsx", sheet = "software")

create_software_sections <- function(type) {
  
  cat("\\vspace{-3mm}")
  
  data <- filter(software, role == type)
  
  type <- stringr::str_to_title(type)
  
  df = data.frame(title = bold(data$main), 
                  desc =  paste0("\\href{", data$link, "}{", data$short_desc ,"}"))
  
  rownames(df) <- nrow(df):1

  print(xtable(df, align = c("l","p{5cm}", "p{10.0cm}"),
                caption = paste0("\\hspace{-5mm}", type)),
        include.colnames = F,
        include.rownames = T,
        floating = TRUE,
        tabular.environment = "longtable",
        sanitize.colnames.function = boldheader)

}
  
software <- software %>% 
  filter(!is.na(short_desc)) %>% 
  select(main, short_desc, homepage, code, role) %>% 
  mutate(link = ifelse(is.na(homepage), code, homepage))

c("Author, Creator", "Author On", "Contributor To") %>% purrr::walk(create_software_sections)

```

Roles as assigned in package description and defined \href{https://journal.r-project.org/archive/2012-1/RJournal_2012-1_Hornik~et~al.pdf}{here}
\vspace{4mm}

\header{INSTRUCTOR, DEPARTMENT OF GEOGRAPHY, UCSB:}
\newline
\hspace*{0mm}
\begin{tabular}{p{3cm}P{13cm}}
\textbf{Summer 2020} & \textbf{Introduction to Geoinformatics}
\vspace{2mm}

\begin{itemize}
  \item Independently developed and taught to address the growing need for data science in the GIS profession.
  \item Will become new prerequisite course for the UCSB Geography Department and new Masters in GIS Curriculum starting in 2021
  \item Content Available here: \textcolor{header_blue}{\textcolor{gray}{\faUniversity} \hspace{0.2mm} \url{https://mikejohnson51.github.io/spds/}}
\end{itemize}
\vspace{2mm}
\end{tabular}

\header{TEACHING ASSISTANT, DEPARTMENT OF GEOGRAPHY, UCSB:}
```{r}
teaching = read_excel("mikes-data.xlsx", sheet = "teaching") %>% 
  filter(type == "Teaching Assisstant")

teaching <- teaching %>%
  mutate(quarter = factor(quarter, levels = c("Fall", "Winter", "Spring", "Summer"), 
                          ordered = T),
         class_link = ifelse(is.na(link), class, 
                             paste0('<a href="',link, '">', class, '</a>'))) %>% 
  group_by(class) %>%
  mutate(points = as.numeric(year) + as.numeric(quarter)/10,
         professor = paste(unique(professor), collapse = ", ")) %>% 
  summarise(year = paste(year,collapse=', '), 
            points = max(points),
            professor = professor[1]) %>% 
  tidyr::unite(data, year, sep = " ") %>% 
  arrange(desc(points)) 

#teaching[1,1] = paste0(teaching[1,1], "\\textsuperscript{1}")
  
col2 <- paste0('{', bold(teaching$class), '}', ' NEWLINE ', 
               teaching$division, " - ", italic(teaching$professor))

df = data.frame(date = bold(teaching$data),
                class = col2)

rownames(df) <- nrow(df):1

print(xtable(df, align = c("l","P{5cm}", "p{12.0cm}")),
      tabular.environment = 'longtable',
      floating = FALSE,
      include.rownames = T)

```

\header{TEACHING AWARD NOMINATIONS, UCSB}
\vspace{-3mm}
```{r}
teaching = read_excel("mikes-data.xlsx", sheet = "teaching_awards") %>% 
  group_by(name) %>% 
  dplyr::mutate(year = bold(paste(year,collapse=', '))) %>% 
  slice(1) %>% 
  select(-sort, -source)

                    
rownames(teaching) <- nrow(teaching):1

print(xtable(teaching, align = c("l","P{3cm}", "p{13cm}")),
      tabular.environment = 'longtable',
      floating = FALSE,
      include.rownames = T)
```

\header{MENTORSHIP EXPERIENCE, UCSB}

\begin{itemize}
  \item Have mentored 11 undergraduates in formal capacities including independent research projects, inclusion in research efforts, and instructional independent study.
  \item Served as a sponsor for the Ronald E. McNair Postbaccalaureate Achievement Program
  \item Serving as a faculty mentor for the Gene and Susan Lucas Undergraduate Research Fund created to help first-generation undergraduate students experience research
\end{itemize}
\vspace{2mm}

\header{PROFESSIONAL EXPERIENCE}
\newline
\hspace*{0mm}
\begin{tabular}{p{4cm}P{13.5cm}}
\textbf{Lecturer} & \textbf{Department of Geography, UCSB} 
\begin{itemize}
  \item Summer 2021 (Offered Position)
\end{itemize}

\vspace{2mm}\\
\textbf{Sep 2019 - Present} & \textbf{Data Scientist}: \href{https://ufokn.github.io/UFOKN/}{Urban Flooding Open Knowledge Network} 
\vspace{2mm}\\
\textbf{Sep 2020 - Present} & \textbf{Water Resourcees Engineer II}*: Lynker Technologies/ NOAA-Affiliate
\begin{itemize}
  \item Assigned to the NOAA Next Generation Water Modeling Engine and Framework Prototype development group
\end{itemize}
\vspace{2mm}\\
\textbf{Visiting Researcher} & \textbf{Institute for Environmental Studies. Vrije Universiteit, Amsterdam}
\vspace{2mm}
\begin{itemize}
  \item June - July 2019
  \item January - March 2018
\end{itemize}
\vspace{2mm}
\textbf{Research Applications Laboratory. NCAR, Boulder, Colorado}
\vspace{2mm}
\begin{itemize}
  \item August - September 2018
\end{itemize}
\vspace{2mm}
\textbf{NOAA National Water Center. Tuscaloosa, Alabama }
\vspace{2mm}
\begin{itemize}
  \item June - August 2017
  \item June - August 2016
\end{itemize}
\vspace{2mm}
\end{tabular}
*security clearance (secret)

\header{PROSFESSIONAL SERVICE}
\vspace{-3mm}
```{r}
experience = read_excel("mikes-data.xlsx", sheet = "experience")

df = data.frame(year = experience$data,
                name = experience$title,
                #details = experience$location,
                sort_year = experience$sort_year)

df3 = df %>% 
  group_by(name) %>% 
  mutate(year = bold(paste0(sort(year, decreasing = TRUE), collapse = ", "))) %>% 
  slice(1) %>% 
  ungroup() %>% 
  arrange(desc(sort_year)) %>% 
  select(-sort_year) %>% 
  data.frame()

rownames(df3) <- nrow(df3):1

print(xtable(df3, align = c("l","p{4cm}", "p{11.5cm}")),
      tabular.environment = 'longtable',
      floating = FALSE,
      include.rownames = T)
```

\newpage
\header{PRESENTATIONS}
```{r}
presentations = read_excel("mikes-data.xlsx", sheet = "presentations")
presentations$blank = ""

col2 <- paste0('{',bold(presentations$location), '}', ' NEWLINE ', italic(presentations$title))

df = data.frame(date = bold(presentations$data),
                title = col2,
                blank = presentations$blank,
                type = presentations$type)

rownames(df) <- nrow(df):1

print(xtable(df, align = c("l","p{2.5cm}", "P{9.5cm}", "p{.5cm}", "P{2cm}")),
      include.rownames = TRUE#,
      #booktabs = TRUE
      )

```

\header{REFERENCES}
\vspace{-3mm}
```{r}
print_ref = function(x, df){
  df[nrow(df) + 1,] = paste0('{', bold(x[1]), '}', 
         ' NEWLINE ', 
         '{', italic(x[2]), '}', 
         ' NEWLINE ',
         '{', italic(x[3]), '}', 
         "\\vspace{2mm}")
  return(df)
}


df = data.frame(
  name = 'Keith Clarke, PhD',
  affil = 'Professor \\newline Department of Geography, University of California, Santa Barbara',
  email = 'kcclarke@ucsb.edu')

df = add_row(df, 
  name = 'Sankar Arumugam, PhD', 
  affil = 'Professor and University Faculty Scholar \\newline Department of Civil, Construction, and Environmental Engineering, North Carolina State University',
  email = 'sankar\\_arumugam@ncsu.edu')

df = add_row(df, 
  name  = 'Krzysztof Janowicz, PhD',
  affil = 'Professor \\newline Department of Geography, University of California, Santa Barbara',
  email ='janowicz@ucsb.edu')

df = add_row(df, 
  name = 'Lilit Yeghiazarian, PhD', 
  affil = 'Associate Professor 
  \\newline Environmental Engineering and Science, University of Cincinnati',
  email = 'yeghialt@ucmail.uc.edu')

df = add_row(df, 
name = 'Trey Flowers, PhD', 
affil = 'Director of the Analysis and Prediction Division \\newline NOAA National Water Center', 
email = 'trey.flowers@noaa.gov') 

df = add_row(df, 
  name = 'David Blodgett', 
  affil = 'Civil Engineer \\newline USGS Office of Water Information Center for Integrated Data Analytics',
email = 'dblodgett@usgs.gov')

df$name = paste0('{', bold(df$name), '} NEWLINE ')
df$affil = paste0('{', (df$affil), '} NEWLINE ')
df$email = italic(df$email)


rownames(df) <- nrow(df):1


print(xtable(data.frame(do.call(paste0, c(df[,1:3]))), align = c("l","p{20cm}"),
        include.colnames = F,
        include.rownames = T,
        floating = TRUE,
        tabular.environment = "tabular",
        sanitize.colnames.function = boldheader))
```