---
name: J Michael
surname: Johnson
position: 'Geographer | Data Scientist | Water Resources'
address: Fort Collins, Colorado
date: "`r format(Sys.time(), '%B, %Y')`"
qualifications: PhD
googlescholar: MrXM9cgAAAAJ
email: 'mikecp11@gmail.com'
www: mikejohnson51.github.io
github: mikejohnson51
linkedin: mikejohnson-phd
fontawesome: yes
docname: Curriculum Vitae
aboutme: As a geospatial data scientist my expertise lies in bridging data‑intensive computational geography with water resources research through open‑source software and data solutions. In both the commercial and federal space, I have led enterprise scale efforts to develop and disseminate foundational datasets supporting research, operational forecasting, and decision‑making across scales. Beyond research, I mentor and teach future scientists as an affiliate at multiple universities and actively publish peer‑reviewed literature to advance the field.
headcolor: 414141
csl: apa7-cv-jy-edition.csl
output: 
  vitae::awesomecv:
    keep_tex: false
    page_total: yes
    pandoc_args: ["--lua-filter=../lua/strong.lua"]
---

```{r setup, include=FALSE}
library(scholar)
library(vitae)
library(stringr)
library(readr)
library(RefManageR)
library(tidyr)
library(dplyr)
library(gsheet)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, error = FALSE)

gs_id = 'MrXM9cgAAAAJ'
mike_gs = get_profile(gs_id) 

cites = get_publications(gs_id) %>% 
   filter(!grepl("AGU|EGU|Meeting|meeting|Preprint|SUMMER INSTITUTE|University|Https|Universities|Frontiers in Hydrology|WaterSciCon|EarthArXiv|Open Archive", journal)) #%>%
   #filter(journal != "")

for(i in 1:nrow(cites)){
  if(!grepl("JM Johnson|J Johnson", cites$author[i])){
    cites$author[i] = get_complete_authors(id = gs_id, pubid = cites$pubid[i])
  }
}

follow = readLines('https://img.shields.io/github/followers/mikejohnson51?label=follow&style=social')

f = str_match(follow, "<title>Follow: \\s*(.*?)\\s*</title>")[,2]

stars = readLines('https://img.shields.io/github/stars/mikejohnson51?affiliations=OWNER%2CCOLLABORATOR%2CORGANIZATION_MEMBER&style=social')

s = str_match(stars, "<title>Stars: \\s*(.*?)\\s*</title>")[,2]

funds = gsheet2tbl('https://docs.google.com/spreadsheets/d/1-Pw8_0NMVJCsD11y8TvFBJXvGHHCLC4F9An5gWWhxqk/edit?gid=631870453#gid=631870453') 

personal = sum(ifelse(is.na(parse_number(funds$subaward)), parse_number(funds$subaward), parse_number(funds$subaward)))
personal = paste0("$", formatC(as.numeric(personal), format="f", digits=0, big.mark=","))

team = sum(parse_number(funds$amount))
team = paste0("$", formatC(as.numeric(team), format="f", digits=0, big.mark=","))
```

# Education

```{r education}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, ~ details,
  "PhD in Geography", "University of California, Santa Barbara", "Santa Barbara, CA", "2021", 
  list("\\textbf{Advisor}: Dr. Keith C. Clarke",
       "\\textbf{Committee}: Hugo Loaiciga, Kelly Caylor, David Blodgett",
       "\\textbf{Title}: Spatial Data Science in Continental Scale Hydrology: 12 Case Studies in Data Models, Data Structures, Modeling, and Evaluation"),
  
  "BS in Anthropology & Geography", "California Polytechnic State University", "San Luis Obispo, CA", "2010 - 2015", 
  list("Cum Laude",
       "Outstanding Senior Award: College of Liberal Arts",
       "\\textbf{Minors}: \\textbf{(1)} GIS for Agriculture \\textbf{(2)} Water Science (Watershed Management) \\textbf{(3)} Statistics \\textbf{(4)} Economics \\textbf{(5)} Environmental Studies")
) %>% 
  detailed_entries(what = loc, 
                   when = dates, 
                   with = uni, 
                   where = degree, 
                   why = details)
```

# Employment

```{r consulting}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  
    "Chief Data Scientist", "Lynker", "Fort Collins, Colorado", "April 2025 - Present", 
     list(),
  
       "Geospatial Science & Technology Lead", "NOAA Office of Water Prediction", "Remote", "Dec 2024 - Mar 2025", 
     list("Led an 8 person Hydrofabric Program advancing hydrologic and flood modeling efforts with geospatial, machine learning, and cloud solutions",
          "In the first 30 days, established a roadmap for the Program, including a comprehensive data management strategy, a cloud-based data dissemination platform, and a collaborative ecosystem for federal, academic, and private partners.",
        'Supplied the methods to reduce the cost of a premier flood mapping service by 60\\% through a novel data pipeline with improved accuracy.',
        "Served as Product Owner and lead developer for mission-critical data assets supporting nearly \\$130 million of investment in the Next Generation Water Resource Modeling Framework Prototype \\& Prediction Capabilities.",
        "Designed and launched spatial.water.noaa.gov, a data dissemination and visualization platform providing seamless access to 2TB of national hydrographic, elevation, and building datasets",
        "Position ended during the 2025 DOGE cuts affecting 880+ probationary NOAA/NWS employees, despite demonstrated impact on national water prediction capabilities."),
  
   "Research & Teaching Affiliate", "Colorado State University", "Fort Collins, CO", "April 2024 - Present", 
     list("Collaborate with researchers and student across the Environmental Science \\& Sustainability Program.",
        "Teach upper division and graduate courses in quantitative reasoning and geospatial data science.", 
        "Host data science interns to support the Professional Science Masters Program."
    ),
  
  "Graduate Faculty (Affiliate)", "University of Alabama", "Remote", "Oct 2023 - Present", 
list("Serve as member or co-chair on dissertation and thesis committees."),
  
  "Chief Data Scientist (Weather & Water Division)", "Lynker", "Fort Collins, Colorado", "Sep 2023 - Dec 2024", 
     list("Pursued business development strategies that secured over \\$15 million in funding to grow a core spatial data program that became a cornerstone of the company's technical portfolio.",
          "Architected innovative geospatial software and data management solutions published in peer-reviewed literature and adopted as enterprise-level systems by NOAA and USGS, significantly advancing federal water resource capabilities.",
          "Designed and maintained a cloud optimized data dissemination platform (lynker‑spatial.com) to support the Next Generation Water Resource Modeling Framework Prototype and Prediction Capabilities by efficiently serving more than 90,000 requests monthly with 99.9\\% reliability."),
  
  "Water Resources Data Scientist", "", "", "Aug 2020 - Sep 2023", 
    list('Supported existing contracts and pursued growth in spatial data programs.',
         "Built, mentored, and retained a high-performing team of 12 data scientists with diverse technical backgrounds.",
         "Established strategic partnerships across federal agencies, research institutions, and private organizations."),
  
  "Hydrofabric Technical Director", "NOAA Office of Water Prediction (Contractor)", "Remote", "Sep 2022 - Dec 2024", 
    list("Led the development of NOAA's Enterprise Hydrofabric solution, supporting multi-scale hydrologic and hydraulic modeling across the Analysis \\& Prediction and Geo-Intelligence Divisions.",
  'Partnered with USGS to develop federal software and data products advancing and aligning NOAA \\& USGS Water Mission Areas.',
  'Contributing author to international standards for hydrologic data, and novel approaches to support modeling, prediction, and evaluation.',
  "Regularly presented OWP's technical progress to agency leadership and the broader community through monthly updates, joint USGS‑NOAA meetings, and scientific conferences."),

"Senior Data Scientist / Lead Hydrofabric Developer", "", "", "Aug 2020 - Present", 
list("Supported NOAA's mission to advance hydrologic prediction capabilities through geospatial science.",
     'Independently prototyped a hydrofabric solution for the Next Generation Water Resource Modeling Framework.'),

"Research Coordinator", "", "", "2016", 
list("Coordinated research activities within the Summer Institute program.",
     'Facilitated collaboration between participants, mentors, and program organizers.',
     'Contributed to the continuous improvement of the program.'),

"Lead Data Scientist (Independent Contractor)", "Urban Flooding Open Knowledge Network", "Remote", "Nov 2019 - Apr 2023", 
    list("Co-authored successful proposals to NSF and served as an advocate for the team in the initial C-ACCEL program",
        "Developed and designed a cost effective, cloud native, building level, flood forecasting system for the Continental United States."),
  
  "Lecturer - Geography Department", "UC Santa Barbara", "Santa Barbara, California", "Summer 2020, 2021", 
    list("Designed and taught the first geoinformatics course for UC Santa Barbara."),

  "", "Visiting Researcher", "Amsterdam, Boulder, Tuscaloosa", "", 
    list("\\textbf{Institute for Environmental Studies. Vrije Universiteit}, Amsterdam, Netherlands: June - July 2019; January - March 2018", 
         "\\textbf{Research Applications Laboratory. NCAR}, Boulder, Colorado: August - September 2018",
         "\\textbf{NOAA National Water Center}. Tuscaloosa, Alabama: Summers of 2016, 2017")

) %>% 
  detailed_entries(role, dates, company, loc, details)
```

# Publications

I actively contribute to the academic literature about the state of my field. \textcolor{cyan}{\href{https://tinyurl.com/mike-google-scholar}{\faicon{google} `r mike_gs$total_cites` citations; \textbf{h-index} `r mike_gs$h_index`; \textbf{i-index} `r mike_gs$i10_index`}}

```{r}
mutate(cites, 
       bibtype = "article",
       number = NA) %>%
  mutate(journal = if_else(journal == "Wiley Interdisciplinary Reviews: Water, e", "Wiley Interdisciplinary Reviews: Water", journal),
         journal = if_else(journal == "Scientific Data", "Nature Scientific Data", journal),
         journal = if_else(journal == "US Geological Survey, Reston, VA, https://doi. org/", "US Geological Survey", journal)) |> 
  as.BibEntry() %>%
  WriteBib("mike-gs.bib")

bibliography_entries("mike-gs.bib") %>%
  arrange(desc(issued))
```

# Funded Work

\textcolor{cyan}{I have personally secured \`r personal` for research \& development and was a key member of teams who collectivly raised \`r team`}

```{r}
funds %>%
  mutate(amount = ifelse(is.na(subaward) | subaward == 0,
                         amount,
                         paste0(amount, " (Subaward: ", subaward, ")"))) %>% 
  detailed_entries(what  = source, 
                   when  = role,
                   with  = name, 
                   where = date)
```

# Knowledge Shareing

\textcolor{cyan}{I have designed and taught data science courses at the lower-division, upper-division, and graduate levels. I was a teaching assistant for over 15 courses. In total, these have supported more than 1,000 students. I have also led community workshops for national organizations and presented at national science meetings.}

## \textcolor{blue}{University Teaching}

```{r}
tribble(
  ~ class, ~ uni, ~ loc, ~ dates, ~ details,
  "Environmental Data Science Applications: Water Resources", "Colorado State University", "Fort Collins, CO", "2025", 
  list("Taught to address the growing need for data science in the Environmental Science profession."),
  
  "Quantative Reasoning for Environmental Science", "Colorado State University", "Fort Collins, CO", "2025", 
  list("Taught to address the growing need for data science in the Environmental Science profession.",
       "\\href{https://mikejohnson51.github.io/ess-csu-330/}{Open course content available here}"),
  
  "Introduction to Geoinformatics", "University of California, Santa Barbara, California", "Santa Barbara, CA", "2021", 
  list("Independently developed and taught to address the growing need for data science in the GIS profession.",
       "Intended to become prerequisite course for the UCSB Geography Department and Masters in GIS Curriculum",
       "\\href{https://mikejohnson51.github.io/spds/}{Open course content available here}")) %>% 
  detailed_entries(what = uni, 
                   when = dates, 
                   with = class, 
                   where = loc, 
                   why = details)
```

## \textcolor{blue}{Teaching Assistant}

```{r}
gsheet2tbl('https://docs.google.com/spreadsheets/d/1-Pw8_0NMVJCsD11y8TvFBJXvGHHCLC4F9An5gWWhxqk/edit?gid=1534465993#gid=1534465993') %>% 
  filter(type == "Teaching Assisstant")  %>%
  mutate(quarter = factor(quarter, levels = c("Fall", "Winter", "Spring", "Summer"), 
                          ordered = T),
         class_link = ifelse(is.na(link), class, 
                             paste0('<a href="',link, '">', class, '</a>'))) %>% 
  group_by(class) %>%
  mutate(points = as.numeric(year) + as.numeric(quarter)/10,
         professor = paste(unique(professor), collapse = ", ")) %>% 
  summarise(year = paste(year,collapse=', '), 
            points = max(points),
            professor = professor[1],
            division = division[1]) %>% 
  unite(data, year, sep = " ") %>% 
  arrange(class) |> 
  # arrange(desc(points)) %>% 
  detailed_entries(professor, division, class, data)
```

## \textcolor{blue}{Invited Presentations / Workshops}

```{r}
presentations = gsheet2tbl('https://docs.google.com/spreadsheets/d/1-Pw8_0NMVJCsD11y8TvFBJXvGHHCLC4F9An5gWWhxqk/edit?gid=272751093#gid=272751093') %>% 
  mutate(Details = ifelse(is.na(Details), character(), Details)) %>% 
  tidyr::separate_longer_delim(Details, "SPLIT") %>% 
  group_by(Title) %>% 
  mutate(Details = list(as.list(Details))) %>% 
  slice(1) %>% 
  ungroup() 

workshops = gsheet2tbl('https://docs.google.com/spreadsheets/d/1-Pw8_0NMVJCsD11y8TvFBJXvGHHCLC4F9An5gWWhxqk/edit?gid=2014229981#gid=2014229981') %>% 
  mutate(Details = ifelse(is.na(Details), character(), Details)) %>% 
  tidyr::separate_longer_delim(Details, "SPLIT") %>% 
  group_by(Title) %>% 
  mutate(Details = list(as.list(Details))) %>% 
  slice(1) %>% 
  ungroup() 

xx = bind_rows(presentations, workshops)

ind = list()

for(i in 1:nrow(xx)){
  ind[[i]] = sum(is.na(unlist(xx$Details[[i]]))) == length(unlist(xx$Details[[i]]))
}

ind = which(unlist(ind))

for(i in 1:length(ind)){ xx$Details[[ind[i]]] = character() }

detailed_entries(arrange(xx, -sort), 
                 what  = Venue, 
                 when  = Type, 
                 with  = Title, 
                 where = Date, 
                 why   = Details,
                 .protect = TRUE)

```

## \textcolor{blue}{Award Nominations}

```{r}
gsheet2tbl('https://docs.google.com/spreadsheets/d/1-Pw8_0NMVJCsD11y8TvFBJXvGHHCLC4F9An5gWWhxqk/edit?gid=518870916#gid=518870916') %>% 
  group_by(name) %>% 
  mutate(year = paste(year, collapse=', ')) %>% 
  slice(1) %>% 
  select(-sort, -source) %>% 
  detailed_entries(where = year, with = name)
```

# Open Source Software

\textcolor{cyan}{A output of my work is open source software in personal \& federal repositories. \href{https://github.com/mikejohnson51}{\faicon{github} \faicon{user} `r f` followers; \faicon{star} `r s` stars}}

```{r}
tribble(
  ~ pkg, ~ role, ~ details,
  "\\href{https://github.com/mikejohnson51/AOI}{AOI}", "Lead Developer", "Fast and flexible geocoding and AOI creation.",
  
  "\\href{https://github.com/mikejohnson51/climateR}{climateR}", "Lead developer", "Instant access to gridded and observation climate data.",
  
  "\\href{https://github.com/mikejohnson51/climateR-catalogs}{climateR-catalogs}", "Lead developer", "A consistent federated data catalog for programmatic access.",
  
  "\\href{https://github.com/mikejohnson51/zonal}{zonal}", "Lead developer", "Fast, flexable spatial data summarization.",
  
  "\\href{https://github.com/mikejohnson51/nwmTools}{nwmTools}",  "Lead developer", "National Water Model Streamflow access.",
  
  "\\href{https://github.com/doi-usgs/nhdplusTools}{DOI-USGS/nhdplusTools}",  "Author", "Manipulating hydrographic data with the NHDPlus data model.",
  
  "\\href{https://github.com/doi-usgs/dataRetrieval}{DOI-USGS/dataRetrieval}",  "Author", "R Interface to the USGS data holdings.",
  
  "\\href{https://github.com/NOAA-OWP/hydrofabric}{NOAA-OWP/hydrofabric}", "Lead Developer", "Generating data products for continental scale hydrology",
  
  "\\href{https://github.com/mikejohnson51/AHGestimation}{AHGestimation}", "Lead Developer", "Estimating robust, mass conserving AHG relationships with cross section hydrualics and geometry",
) %>%
  detailed_entries(when = role, 
                   with = pkg,
                   what = details, 
                   .protect = FALSE)
```
